Untitled

### 2019-08-12 IPCO_NS.Rmd
updated

---
title: "Untitled"
author: "NSharma"
date: "5 May 2016"
output: html_document
---

@@

	library(foreign)
	library(stargazer)
	library(psych)
	library(plyr)
	library(xtable)
	library(car)
	#library(dplyr)
	library(scales)
	library(reshape) 
	library(gmodels)
	library(nnet)
	library(tidyr)
	library(sjmisc)
	library(RColorBrewer)
  library(htmltools)
	library(broom)

@@

#Do normalisation/transform as suggested as an where required. If the phyloseq data is already normalised and doesnot wish to renormalise, then the user doesnot have to follow IPCO normalisation.
#We recommend Hellinger transformation. To be used on count/prop/relative abundance data
ref_genus <- transform_data(IPCO_Healthy$Genus,"relab")
ref_func <- transform_data(IPCO_Healthy$MetaCyc,"prop")
##or
ref_func <- transform_data(IPCO_Healthy$KEGG,"prop")

#if query genus table is count data
query_genus <- transform_data(genus_table,"count")

#Run IPCO
#Note: all samples should be in columns and features (func/taxa) in rows. If not, transpose the matrix
inferred_MetaCyc <- IPCO(ref_func,ref_genus,query_genus)

data <- data("IPCO_Healthy")

write_phyloseq(pseq, type = "all", path = getwd())

tdata <- transform_data(data, type = "proportion")
tdata <- transform_data(IPCO_Healthy, proportion)

@@

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "Untitled"
author: "NSharma"
date: "2019"
output: html_document
---

@@

@@

#Do normalisation/transform as suggested as an where required. If the phyloseq data is already normalised and doesnot wish to renormalise, then the user doesnot have to follow IPCO normalisation.

#We recommend Hellinger transformation. To be used on count/prop/relative abundance data
ref_genus <- transform_data(IPCO_Healthy$Genus,"relab")
ref_func <- transform_data(IPCO_Healthy$MetaCyc,"proportion")

#ref_func <- filter_functionality(ref_func, "metacyc",IPCO_Healthy$MetaCyc_coverage,threshold=0.4) # Filtering

ref_func <- filter_functionality(ref_func, "metacyc", IPCO_Healthy$MetaCyc_coverage)
##or
#ref_func <- transform_data(IPCO_Healthy$KEGG,"proportion")

#if query genus table is count data
#query_genus <- transform_data(genus_table,"count")

#Run IPCO
#Note: all samples should be in columns and features (func/taxa) in rows. If not, transpose the matrix
inferred_MetaCyc <- IPCO(ref_func,ref_genus,genus_table)

library(made4)

overview(inferred_MetaCyc)

k.coa<- ord(inferred_MetaCyc, type="coa")
summary(k.coa$ord)

plotgenes(k.coa)

heatmap(inferred_MetaCyc)

p <- plot_ly(inferred_MetaCyc = volcano, type = "heatmap")

levelplot(inferred_MetaCyc[1:ncol(inferred_MetaCyc),ncol(inferred_MetaCyc):1])

coinertia_resuls <- check_coinertia(ref_func,genus_table)

@@
